### 2018-12-27 Sections/intro_to_QM.tex
minor

The described formalism in terms of measurement projectors gives us `singe-shot' information about measurement -- what is the probability of a given single measurement outcome, and what is the state of the system following this measurement? Alternately, we might be interested not in single-shot events, but statistical measurement information, such as the average measurement outcome.

We define a measurement \textit{observable}\index{Observable} as an operator $\hat{O}$ acting on a state-space, with eigenvalues $O_i$ over some range of $i$. The eigenvalues $O_i$ denote the allowed values of the measurement outcome for the associated eigenstate, which corresponds to the projected post-measurement state. The statistical expectation value\index{Expectation value} of these measurement outcomes for a given state $\ket\psi$ may now be obtained as,
\begin{align}
	\braket{\hat{O}} = \braket{\psi|\hat{O}|\psi},
\end{align}
and their variance\index{Variance} by,
\begin{align}
	\braket{\hat{O}^2} - \braket{\hat{O}}^2.
\end{align}

>>>>

The described formalism in terms of measurement projectors gives us `singe-shot' information about a measurement -- what is the probability of a given single measurement outcome, and what is the state of the system following this measurement? Alternately, we might be interested not in single-shot events, but statistical measurement information, such as the average measurement outcome in the limit of a large number of repeated independent trials.

We define a measurement \textit{observable}\index{Observable} as an operator $\hat{O}$ acting on a state-space, with eigenvalues $O_i$ over some range of $i$. The eigenvalues $O_i$ denote the allowed values of the measurement outcome for the associated eigenstate, which corresponds to the projected post-measurement state. The statistical expectation value\index{Expectation value} of these measurement outcomes for a given state $\ket\psi$ may now be obtained as the expectation value of the observable,
\begin{align}
	\braket{\hat{O}} = \braket{\psi|\hat{O}|\psi},
\end{align}
and their variance\index{Variance} by,
\begin{align}
	\braket{\hat{O}^2} - \braket{\hat{O}}^2.
\end{align}
Both of these are in the limit of an infinite number of independent trials of the measurement on identical copies of the state.
